GMSE: an R package for generalised management strategy evaluation

### 2017-08-09 notebook/ms/ms.Rmd
Some progress on the genetic algorithm section

Game theory is the standard tool for understanding conflict between rational agents, and is therefore the appropriate tool for modelling stakeholder actions and addressing issues of cooperation and conflict in conservation [@Colyvan2011; @Lee2012; @Kark2015; @Adami2016; @Tilman2016]. A game-theoretic approach is compatible with agent-based modelling [@An2012; @Tesfatsion2017], but given the number of possible strategies available to agents, identifying optimal strategies is often intractable. Instead, genetic algorithms, which mimic the process of natural selection (mutation, recombination, selection, reproduction), are useful to find adaptive solutions for game strategies [e.g., @Balmann2000; @Tu2000; @Hamblin2013].

>>>>

Game theory is the formal study of strategic interactions, and can therefore be applied to modelling stakeholder actions and addressing issues of cooperation and conflict in conservation [@Colyvan2011; @Lee2012; @Kark2015; @Adami2016; @Tilman2016]. In game-theoretic models, agents adopt strategies to make decisions that maximise some type of payoff (e.g., utility, biological fitness). Agents are constrained in their decision-making, and realised pay-offs depend on decisions made by other agents. In simple models, it is often useful to assume that agents are perfectly rational decision-makers, then find optimal solutions for pay-off maximisation mathematically. But models that permit even moderately complex decision-making strategies or pay-off structures often include more possible strategies than are mathematically tractable [@Hamblin2013]. In these models, genetic algorithms, which mimic the process of natural selection (mutation, recombination, selection, reproduction), can find adaptive (i.e., practical, but not necessarily optimal) solutions for game strategies [e.g., @Balmann2000; @Tu2000; @Hamblin2013].

Consistent with the MSE approach [@Bunnefeld2011], GMSE does not attempt to find optimal strategies or solutions for agents (stakeholders). Instead, genetic algorithms are used to find an adaptive strategy for each stakeholder in each time step.

A game-theoretic approach is compatible with agent-based modelling [@An2012; @Tesfatsion2017], but given the number of possible strategies available to agents, identifying optimal strategies is often intractable. Instead, genetic algorithms, which mimic the process of natural selection (mutation, recombination, selection, reproduction), are useful to find adaptive solutions for game strategies [e.g., @Balmann2000; @Tu2000; @Hamblin2013].
